The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2015-12-26 article.tex
More detail about the deps figure
Overview of key modules and their dependencies

% FIXME: add dependency plot

@@

\section*{Figures}
  \subsection*{Figure 1 - Dependencies between CDK modules.}
  \label{fig:deps}
      Visualization of the dependencies between CDK modules. For example,
      the cdk-core depends on the cdk-interfaces module.

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - The molecular fingerprints in CDK}
  \label{tab:fingerprints}
  Listed are the currently available molecular fingerprint in CDK with
  information about whether they come as bit / count versions, what CDK version
  they appeared in, their default size and where applicable also relevant
  references.
  \vskip 1\baselineskip

>>>>

An overview of key modules with description, important changes, and dependencies
on third-party libraries is given in Table~\ref{tab:modules} and the dependencies
between the CDK modules are depicted in Figure~\ref{fig:deps}.

@@

\section*{Figures}
  \subsection*{Figure 1 - Dependencies between CDK modules.}
  \label{fig:deps}
      Visualization of the dependencies between CDK modules. For example,
      the cdk-core depends on the cdk-interfaces module. A few higher level
      modules have been left out: cdk-builder3dtools, cdk-legacy, and
      cdk-depict.

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}

  \subsection*{Table 1 - A selection of key CDK modules with major changes.}
  \label{tab:modules}
  An overview of a selection of often used CDK modules with description,
  dependencies on third-party libraries, and the major changes since
  version~1.2. Depedencies between modules are depicted in Figure~\ref{fig:deps}.
  \vskip 1\baselineskip

    \begin{minipage}{1\textwidth}
    \renewcommand*{\thempfootnote}{\fnsymbol{mpfootnote}}
    \centering
    \begin{tabular}{llll}
  Module                     & Description  & Major Changes & Depedencies \\
  interfaces                 &              & & Vecmath 1.5.2 \\
  core                       &              & & Google Guava 17.0 \\ % FIXME: how to add https://github.com/google/guava ?
  standard                   &              & & \\
  render                     &              & Redesigned to make it more modular and support multiple widget toolkits, like AWT and SWT. & \\
  isomorphism                &              & & \\
  atomtype                   &              & Unified approach where atom typing is separated from other algorithms. & \\
  valencycheck               &              & & \\
  ioformats                  &              & & \\
  io                         &              & The MDL molfile reader has been rewritten and supports in atom types defind in the specification. & XPP3 1.1.4c \\
  iordf                      &              & New. & Jena 2.7.4 \\
  inchi                      &              & & JNI-InChI 0.8~\cite{Spjuth2013}  \\
  libiocml                   &              & & XOM 1.2.5, CMLXOM 3.1~\cite{Murray-Rust2011} \\
  smiles                     &              & SMILES support performance and converage is greatly improved. & Beam 0.9.1 \\ %FIXME add a citation
  smarts                     &              & & Beam 0.9.1 \\ %FIXME add a citation
  formula                    &              & New. & \\
  fingerprint                &              & Many new fingerprint types (see text). & Apache Commons Math 3.1.1 \\
  qsar                       &              & & XOM 1.2.5, JAMA 1.0.3~\cite{Hicklin2012} \\ % FIXME: find JAMA reference
  signatures                 &              & & Signatures 1.1 \\ % FIXME: ask Gilleain for the reference
  qsarmolecular              &              & & \\
  log4j                      &              & & Log4j 1.2.17 \\
    \end{tabular}
    \end{minipage}

  \subsection*{Table 1 - The molecular fingerprints in CDK.}
  \label{tab:fingerprints}
  Listed are the currently available molecular fingerprint in CDK with
  information about whether they come as bit / count versions, what CDK version
  they appeared in, their default size and where applicable also relevant
  references.
  \vskip 1\baselineskip
